Gaia DR2 view of the GD-1 stellar stream

### 2018-04-27 paper/gd1.tex
words

\begin{abstract}\noindent % trust me
Tidally-disrupted globular clusters leave behind thin, dynamically-cold streams
of stars that are extremely valuable tracers of the large- and small-scale
properties of mass around the Galaxy.
Many thin stellar streams have been discovered around the Milky Way, the
majority of which exist in the Galactic halo and are therefore primarily
sensitive to the distribution of dark matter.
Here we present astrometric data for one of the longest stellar streams --- the
``GD-1'' stream --- from data release 2 (\DR) of the \gaia\ mission.
We re-discover significant density variations along the stream by selecting
candidate member stars using the exquisite \gaia\ data alone, including the
existence of a prominent, apparent gap in the stream.
<Using photometric data from the \pans, we refine our selection ...>
These density variations --- and especially the gap --- are possible indications
of past interactions with large, massive perturbers.
<estimate the mass of interaction...>
\end{abstract}

>>>>

\begin{abstract}\noindent % trust me
Tidally-disrupted globular clusters leave behind thin, dynamically-cold streams
of stars that are extremely valuable tracers of the large- and small-scale
properties of mass around the Galaxy.
Many thin stellar streams have been discovered around the Milky Way, the
majority of which exist in the Galactic halo and are therefore primarily
sensitive to the distribution of dark matter.
Here we present astrometric data for one of the longest stellar streams --- the
``GD-1'' stream --- from data release 2 (\DR) of the \gaia\ mission.
We re-discover significant density variations along the stream by selecting
candidate member stars using the exquisite \gaia\ data alone.
Combined with filtering using Pan-STARRS photometry, we see clear evidence of a
prominent, apparent gap in the stream, and at least XX other under-densities.
These density variations --- and especially the gap --- are possible indications
of past interactions with large, massive perturbers such as dark matter
sub-halos.
\end{abstract}
